Testing perceptual accuracy in a U.S. general population survey using stacked bar charts

### 2023-12-21 SDSS-2023/testing-charts-accuracy.tex
updating supplementary materials header for page limit

\hypertarget{supplementary-material}{%
\section{Supplementary Material}\label{supplementary-material}}

The source code and data used in this paper are available on a GitHub
repository at \url{https://github.com/kiegan/testing-charts-jds}. In
addition, we provide an example stimulus image in that repository.

>>>>

\hypertarget{supplementary-material}{%
\section*{Supplementary Material}\label{supplementary-material}}
\vspace{-4mm}

The source code and data used in this paper and an example stimulus image are available on a GitHub
repository at \url{https://github.com/kiegan/testing-charts-jds}.
